\documentclass[11pt]{resume}
\renewcommand{\categoryfont}{\sc}
\usepackage[final]{pdfpages}
\usepackage{bibunits}

\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}
%
\addtolength{\marginparwidth}{-\marginparsep}
\setlength{\evensidemargin}{\oddsidemargin}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}
\addtolength{\textwidth}{-2\oddsidemargin}
\addtolength{\textwidth}{\marginparwidth}
\addtolength{\textwidth}{\marginparsep}
%
\setlength{\topmargin}{-0.5in}
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\author{Ketan C Maheshwari}
% ------ Address --------------------------------------------------------

\address{\mbox{\small\tt km0@ornl.gov}\\
	}{ Knoxville,\\ TN 37934 USA\\}	
\begin{document}
% \includepdf[pages=1-1]{cover_letter.pdf}
\maketitle


%--------------------------------objective-----------------------------------------------------
%\begin{category}{Objective}
%\citemnobullet To work on challenges pertaining to HPC systems.
%\end{category}

% ----------------------------- Education ------------------------------------------------------
\begin{category}{Education}
\citem{University of Nice at Sophia Antipolis}, France.\\
PhD with \textbf{Highest Honors}, January 2011.\\
Research on parallel workflow expression and enactment on large-scale
distributed computing infrastructures for data intensive applications. 

%======================================================================================

\citem{University of Amsterdam}, Amsterdam, The Netherlands.\\
Research M.Sc.(NVAO-accredited) in Grid Computing, August 2007.\\
\textbf{Masters Thesis Work}\\
To achieve integration and interoperability among several Workflow Management Systems and Problem Solving Environments (PSE) in order to realize a Medical Image Analysis Support System at the University of Amsterdam Academisch Medical Centrum, Amsterdam.\\
\citem{Gujarat University}, Ahmedabad, India.\\
Masters in Computer Applications (MCA), September 2001.\\
\textbf{Major Courses}: Fundamentals of Programming, Database Systems, Operating Systems, Data and File Structures, Object Oriented Analysis and Design, Discrete Mathematical Structures, Numerical Methods, Software Engineering, Client Server Technologies, Networking Technologies, Computer Architecture.
\citem{Gujarat University}, Ahmedabad, India.\\
Bachelors in Science, June 1998.
\end{category}

% ---------------------------------- Work experience ---------------------------------------------

\begin{category}{Work}
\citem{Linux Systems Engineer} Oak Ridge National Laboratory, 2017 - current.

\citem{HPC Consultant} Center for Research Computing, University of Pittsburgh, 2016 - 2017.
Application development and deployment, source code debugging, expert and dedicated HPC user support,
implementation and management of Petabyte ZFS storage system, gave workshops on R, CUDA, advanced Linux and Python.

\citem{Postdoctoral Researcher} Distributed Systems Lab, Argonne National
Laboratory, 2011 - 2016.\\
Supporting large-scale applications on HPC infrastructures, user-engagement
catalyst and researcher for HPC and HTC infrastructures. Main activities
include developing, deploying and running parallel applications over IBM BG/Q,
Cray XE6 and Intel supercomputers, clusters and clouds. Applications
include protein docking, fMRI image processing, energy systems,
seismology simulation, and power grid modelling. Funded by NSF, DOE and
NIH.

\citem{ICT Developer} Informatics Institute(IvI), University of
Amsterdam(UvA), 2006 to 2007.\\
Globus File Transfer integration to
achieve transfer of large number of big files between Academisch Medical
Centrum (AMC) and Storage Resource Broker (SRB) at SARA, Amsterdam. Integrated
with a Visual Resource Browser.

\end{category}

\begin{category}{Synergistic Activities}
\citem{FEMA COVID-19 Support.} Active support of FEMA sponsored COVID-19 research in collaboration with Johns Hopkins researchers. \emph{2020 Lab Director's Award winner for this work}
\citem{Federated Id.} Multi-lab Collaboration as part of the Distributed Compute and Data Ecosystem (DCDE) undertaking research in federation of identities. 
\citem{Workflow Research.} Collaborative inter-division workflow research with Nuclear Sciences Division at Oak Ridge.
%\citem{Courses} taught Operating Systems, Java and C++ courses to undergrad students during PhD at Univ of Nice in 2010. 
%\citem{Seminar} at the League of Professional System Administrators (LOPSA) East Tennessee in 2018.
\end{category}

%------------------------ Certification -------------------------------------------------
\begin{category}{Awards}
\citembullet~~Lab Director's Award for COVID-19 research Tech support (2020)
\citembullet~~First winner at Smokey Mountain Data Challenge (2018)
\citembullet~~\textbf{RedHat Certified System Administrator} (190-042-697)
\end{category}

%\newpage
% ------- Skills ------------------------------------------------------
\begin{category}{Skills}
\citembullet Expertise in HPC toolchains, compilers, debuggers, schedulers, storage, network
\citembullet Expertise and experience in development and deployment of workflows to support leadership scale science, container management, Kubernetes
\citembullet Linux, ranked top 3~\% of Linux StackExchange Community (Jan 2021)
\end{category}

\bibliographystyle{unsrt}
\renewcommand\refname{Relevant Publications \& Presentations}
\bibliography{selectedpub}
\nocite{*}
% \includepdf[pages=1-1]{cover_letter.pdf}
\end{document}
