\documentclass{report}

\pagenumbering{gobble}
\usepackage[english]{babel}
\usepackage[pdftex]{color,graphicx}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\setlist[itemize]{leftmargin=*,noitemsep}
\usepackage[T1]{fontenc}

\title{Scientific Software Installation in the User Space\\
       \large A tutorial proposal for PEARC'21
			 }

\author{Ketan Maheshwari and Hong Liu}

\begin{document}
\maketitle
\section*{Abstract}
We propose to offer a comprehensive, definitive and clarifying tutorial on the
process and practice of scientific software building, installation,
configuration and setup in the \emph{user-space} for large-scale computational
infrastructures.

\section*{Detailed description}
Scientific software installation process is often taken for granted.
Installations often end up being suboptimal resulting in an underperforming
software. Furthermore, a subpar installation often undergoes through erratic
post-install configuration, patches, etc. causing further degration.

As the technical installation process varies from software to software, it gets
difficult and tedious process that discourages users from installing some
packages. This results in users stuck with older versions of software
preventing them from using the newer features. In many cases, users rely on
sysadmins for tedious installs but since users are many and sysadmins are
limited in number, this either causes substantial delays or limited installs. 

With the advent of the python ecosystem, and a number of supported install methods
the waters have muddied quite a bit that often makes users resisting installing
software or face difficulties after a faulty installation due to conflicting methods.

Our tutorial is a result of 10+ years of combined experience installing and
setting up a wide variety of software packages for self and users over a number
of cluster and supercomputing environments. We bring clarity to the various
software installation paradigms and give structure to an often perceived
chaotic process.

\subsection*{Tutorial goals}
\begin{enumerate}
\item To comprehensively cover, document and present all the facets of the process and practice of scientific software installation.
\item Share knowledge of scientific software installation in user space over compute clusters and supercomputers.
\item Demonstrate best practices for software installation.
\item Clarify the concepts, principles and patterns found in the software installation process.
\item Present plenty of practical and hands-on examples of contemporary scientific software installation process.
\end{enumerate}

\subsection*{Relevance of topic to conference attendees}
We believe the topic is relevant and useful to conference attendees. The following scenarios support our belief:
\begin{itemize}
\item A researcher experimenting with several versions of a software library would like to efficiently install them in their home area.
\item A scientist who extends a popular scientific software and would like to link it to a cluster installed library.
\item Users who would like to use specialized compilers such as NAG or PGI that are not always available systemwide.
\item Users who would like to supplement the system installed libraries for GPUs with their own Kokkos driven codes.
\end{itemize}

\subsection*{Targeted audience}
\begin{itemize}
\item System administrators and managers who might want to re-use the tutorial for the users of their home cluster environment.
\item Science users will benefit with the clear understanding of the process of software installation crystalized and clarified.
\end{itemize}
\subsection*{Content level (\% beginner, \% intermediate, \% advanced)}
80 \% Beginner, 10 \% intermediate, 10 \% advanced
\subsection*{Audience prerequisites}
Basic knowledge and hands-on experience on Linux command-line. Understanding of
basic Linux concepts such as paths, files and directories, permissions etc.

\section*{Detailed outline of the tutorial}
\begin{enumerate}
\item Overview and Logistics
  \begin{itemize}
    \item Motivation: why yum / apt / dnf does not work? 
    \item Slides and Practice Software Packages download
  \end{itemize}
\item The Make Basics
  \begin{itemize}
    \item Anatomy
    \item Functionality and Pitfalls
  \end{itemize}
\item The configure, make, make test, make install workflow
  \begin{itemize}
    \item Configure Concept
    \item Configure Script
    \item Configure Examples
    \item Make and Make Install nitty-gritty
    \item Post-install setup
  \end{itemize}
\item The ccmake, cmake, make workflow
    \begin{itemize}
      \item cmake Fundamentals
      \item cmake Troubleshooting and examples
    \end{itemize}
\item Compilers times Libraries times Versions Combinatorics
  \begin{itemize}
    \item How to manage efficiently
    \item Updates and upgrades
  \end{itemize}
\item The Python Zoo
  \begin{itemize}
    \item 2 vs 3 implications
    \item pip / pip3 and conda
    \item setup.py and wheel
    \item requirements.txt
    \item environment and virtual env
    \item update / upgrade
    \item Tips and Tricks
  \end{itemize}
\item Other Software Installation Methods
    \begin{itemize}
        \item spack and easy\_install
        \item rubygems, npm, luarocks, cargo
        \item Apache ant, Maven, SCons, ninja 
        \item rpm and binary installs
    \end{itemize}
\item Miscellaneous Tips
  \begin{itemize}
    \item Use session managers for long builds
    \item Save logs and successful commands
    \item System architecture and other considerations
  \end{itemize}
\item Summary and Conclusions
  \begin{itemize}
    \item A handy cheatsheet to take home
  \end{itemize}
\end{enumerate}

\subsection*{A statement about ``hands-on'' exercises}
Each section in the tutorial will have hands-on exercises. The hands on exercises are based on:
\begin{enumerate}
\item The ideas and concepts discussed in the section 
\item Free and open-source science software that are popularly used
\end{enumerate}
We will provide the solutions to hands-on exercises to students at the end of the tutorial.

\subsection*{Resume or CV for each presenter}
Attached.
%\subsection*{A statement agreeing to release the notes for the SC18 tutorial digital copy}
%I agree to release the notes for the SC18 tutorial digital copy.

\end{document}

Introduction

Plan

Audience and Benefits

yum, apt, dnf etc. are ok on VMs and Desktops but not on clusters. Why?

Understanding a Makefile and make commands
VERBOSE and parallel with -j
troubleshoot

autotools autoconf
    troubleshoot

configure; make; make install
    troubleshoot

ccmake, cmake, make && make install
    troubleshoot

Environment variables

Compilers times Libraries times versions

update / upgrade software

The python zoo

userspace rpms
    rare but possible

dangers and pitfalls
system-level libraries
best practices

java ant apache build

binary installations

